---
title: "Intro Data Science"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: https://github.com/mine-cetinkaya-rundel/wtf-teach/blob/master/student-dashboard/student-dashboard.Rmd
    theme: bootstrap
---

```{r setup}
library(flexdashboard)
library(tidyverse)
library(wordcloud)
library(tidytext)
```

# Individual students

## Inputs {.sidebar}

```{r}
student_survey <- read_csv("Getting to know you - 2021 Diversity Scholars (Responses) - Form Responses 1.csv")

names(student_survey) <- c(
  "timestamp",
  "cohort", 
  "name",
  "preferred_name",
  "pronounciation",
  "pronouns", 
  "unique",
  "know_other",
  "learn_best",
  "fav_class",
  "took_course",
  "taught_course",
  "songs",
  "learn_goal",
  "concern",
  "clarify"
)

student_survey <- student_survey %>%
  arrange(name)

student_survey <- bind_rows(
  student_survey %>% filter(name == "Mine Cetinkaya-Rundel"),  
  student_survey %>% filter(name != "Mine Cetinkaya-Rundel"),  
)

student_survey <- student_survey %>%
  mutate(
    cohort = if_else(str_detect(cohort, "Cohort A"), "A", "B")
  )
```

```{r}
selectInput(inputId = "student",
            label = "Select a student",
            choices = student_survey$name)
```

```{r}
selected_student <- reactive({
  student_survey %>%
    filter(name == input$student)
})
```

```{r eval=FALSE}
renderImage(
  list(src = paste0("www/", input$student, ".png"),
       contentType = "image/png",
       width = 230),
  deleteFile = FALSE
)
```

## Row

### Preferred name {.value-box}

```{r}

renderValueBox({
  preferred_name <- selected_student() %>%
    select(preferred_name)
  valueBox(
    value = preferred_name,
    icon = "fa-portrait"
  )
})
```

### Pronouns {.value-box}

```{r}
renderValueBox({
  pronouns <- selected_student() %>%
    mutate(pronouns = if_else(is.na(pronouns), "", pronouns)) %>%
    select(pronouns)
  valueBox(
    value = pronouns,
    icon = "fa-user-check",
    color = "info"
  )
})
```

### Cohort {.value-box}

```{r}
renderValueBox({
  cohort <- selected_student() %>%
    mutate(cohort = if_else(is.na(cohort), "", cohort)) %>%
    select(cohort)
  valueBox(
    value = cohort,
    icon = "fa-user-friends",
    color = "info"
  )
})
```

## Row

### Pronounciation {data-width="200"}

```{r}
renderText(selected_student()$pronounciation)
```

### Hope to learn... {data-width="200"}

```{r}
renderText(selected_student()$learn_goal)
```

### Took course before? {data-width="200"}

```{r}
renderText(selected_student()$took_course)
```

### Taught course before? {data-width="200"}

```{r}
renderText(selected_student()$taught_course)
```

## Row

### Anything else you would like me to know about you? {data-width="500"}

```{r}
renderText(selected_student()$know_other)
```

## Row

### Something cool / unique about yourself {data-width="200"}

```{r}
renderText(selected_student()$unique)
```

## Row

### How do you learn best? {data-width="500"}

```{r}
renderText(selected_student()$learn_best)
```

## Row

### What, if anything, concerns you about this course? {data-width="500"}

```{r}
renderText(selected_student()$concern)
```

# Overall

## Row

### Have you taken an R course before? {data-width="200"}

```{r fig.width = 10}
ggplot(student_survey, aes(x = took_course, fill = took_course)) +
  geom_bar() +
  coord_flip() +
  scale_fill_viridis_d() +
  guides(fill = "none") +
  labs(x = "", y = "") +
  theme_minimal() +
  theme(text = element_text(size = 22))
```

### Have you taught an R course before? {data-width="200"}

```{r fig.width = 10}
ggplot(student_survey, aes(x = taught_course, fill = taught_course)) +
  geom_bar() +
  coord_flip() +
  scale_fill_viridis_d() +
  guides(fill = "none") +
  labs(x = "", y = "") +
  theme_minimal() +
  theme(text = element_text(size = 22))
```

## Row

### What, if anything, concerns you about this course? {data-width="200"}

```{r}
pal <- brewer.pal(4, "Blues")
```

```{r}
student_survey %>%
  select(concern) %>%
  unnest_tokens(word, concern) %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, random.order = FALSE, colors = pal))
```

### Is there anything you would like me to clarify about the course? {data-width="200"}

```{r}
student_survey %>%
  select(clarify) %>%
  unnest_tokens(word, clarify) %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, random.order = FALSE, colors = pal))
```
